# Activity Monitoring Devices

### 1.Loading and preprocessing the data
Code:
```{r load_data, echo=TRUE}
setwd("C:/Users/Ivan.Liuyanfeng/Desktop/Data_Mining_Work_Space/Reproducible_research/")
act.zip <- "activity.zip"
act.csv <- "activity.csv"
if(file.exists(act.zip)) unzip(act.zip)
act.data <- read.csv(act.csv, header=TRUE)
library(data.table)
tb.data <- data.table(act.data)
act.total <- tb.data[,sum(steps,na.rm=T),by=date]
head(act.total,n=5)
```

### 2.What is mean total number of steps taken per day?
2.1 Make a histogram of the total number of steps taken each day.
```{r hist_step, echo=TRUE, fig.height=3, fig.width=6}
library(ggplot2)
setnames(act.total, "V1","steps")
hist.s <- qplot(steps, data=act.total)
hist.s + labs(title="Total Number of Steps")
```

2.2 Calculate and report the mean and median total number of steps taken per day.
```{r avg_step,echo=TRUE}
step.mean <- mean(act.total$steps,na.rm=T)
step.median <- median(act.total$steps, na.rm=T)
```
##### The mean and median total number of steps taken per day are `r step.mean` and `r step.median`, respectively.

### 3.What is the average daily activity pattern?
3.1 Make a time series plot of the 5-minute interval and the average number of steps taken, averaged across all days.
```{r time_series, echo=TRUE, fig.height=3, fig.width=6}
act.avg <- tb.data[,mean(steps,na.rm=T),by=interval]
setnames(act.avg, "V1","steps")
ts <- ggplot(act.avg, aes(x=interval,y=steps))
ts + geom_line() + labs(title = "Average Number of Steps across All Days")
```

3.2 Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r max_step, echo=TRUE}
step.max <- act.avg$interval[act.avg$steps==max(act.avg$steps)]
```
##### The 5-minute interval:  `r step.max`, contains the maximum number of steps on average across all the days in the dataset.

### 4.Imputing missing values
4.1 Calculate and report the total number of missing values in the dataset.
```{r missing_value, echo=TRUE}
num_missing <- sum(is.na(act.data[,1]))
```
##### The total number of missing values in the data set is: `r num_missing`!

4.2 Devise a strategy for filling in all of the missing values in the dataset.
```{r imputation, echo=TRUE}
imputed.data <- act.data
for (i in 1:nrow(act.data)){
        if (is.na(imputed.data[i,1])){ imputed.data[i,1] <- mean(act.data$steps, na.rm=T)}
}
```

4.3 Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r data_proc, echo=TRUE}
tb.imputed <- data.table(imputed.data)
imputed.total <- tb.imputed[,sum(steps,na.rm=T), by=date]
```

4.4 Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r hist_imputed, echo=TRUE, fig.height=3,fig.width=6}
#colnames(imputed.total)
setnames(imputed.total, "V1","steps")
hist.s.2 <- qplot(steps, data=imputed.total)
hist.s.2 + labs(title="Total Number of Steps (Imputed)")
step.mean.imputed <- mean(imputed.total$steps, na.rm=T)
step.median.imputed <- median(imputed.total$steps, na.rm=T)
```
The mean and median total number of steps taken per day are `r step.mean.imputed` and `r step.median.imputed` !

### 5.Are there differences in activity patterns between weekdays and weekends?
5.1 Create a new factor variable in the dataset with two levels.
```{r factor_var, echo=TRUE}
a <- as.character(imputed.total$date)
b <- strptime(a,"%Y-%m-%d")
c <- weekdays(b)
imputed.total$weekday <- c
```

5.2 Make a panel plot containing a time series plot of the 5-minute interval and the average number of steps taken.
```{r, echo=TRUE}

```
